---
title: "garbage"
author: "Jack Conner"
date: "2023-10-05"
output: html_document
---
```{r}
716 %/% 7
716 %% 7
high_school_1600_times <- c(306.21, 299.51, 298.98, 294.35, 279.5, 277.8, 287, 282.31, 275.9, 276.69, 272.84, 271.45, 272, 277.97, 268.21, 267.82, 275.37)

mean(high_school_1600_times)
freshman_1600_times <- high_school_1600_times[1:4]
sophomore_1600_times <- high_school_1600_times[5]
junior_1600_times <- high_school_1600_times[6:9]
senior_1600_times <- high_school_1600_times[10:17]
avg_freshman_1600 <- mean(freshman_1600_times)
avg_sophomore_1600 <- mean(sophomore_1600_times)
avg_junior_1600 <- mean(junior_1600_times)
avg_senior_1600 <- mean(senior_1600_times)

max(high_school_1600_times)
min(high_school_1600_times)

high_school_1500_conversion <- high_school_1600_times - 20
high_school_1500_conversion

senior_1500_times <- high_school_1500_conversion[10:17]
mean(senior_1500_times)

avg_freshman_1600 - avg_sophomore_1600
avg_sophomore_1600 - avg_junior_1600
avg_junior_1600 - avg_senior_1600
avg_freshman_1600 - avg_senior_1600
avg_junior_1600

length(junior_1600_times)
length(senior_1600_times)

senior_1600_times / 4

m1data <- c(1, 2, 7, 4, 3, 3, 9, 12, 0, 12, 4, 35)

matrix_1 <- matrix(data = m1data, nrow = 3, ncol = 4)
matrix_1

c
-2:0
pi
TRUE
log(c(2, 4, 5)) - exp(3)
1:3 + 2:5
x <- c(2, 3, 4, 5, 5)



x <- c(70, 4, "NA")
logical(length(x))
```

```{r}
num_orders <- matrix(1:100, nrow = 10, ncol = 10)
food_items <- c("Burrito", "Taco", "Quesedilla")
food_items <- factor(food_items)
food_items <- matrix(c("Burrito", "Taco", "Quesedilla"), nrow = 10, ncol = 10)
tapply(num_orders, food_items, sum)
```

```{r}
class(parks_df)
X <- matrix(1:4, nrow = 2, ncol = 2)
class(X)
L <- list("First Component" = matrix(1:8, nrow = 4, ncol = 2), "Last Component" = c(1, 7, 4, 3))
with(L, 'Last Component')
with(L, "Last Component")
```

```{r}
parks_mat <- cbind(c(62, 71, 66), c(115, 201, 119), c(4000, NA, 2000))
rownames(parks_mat) <- c("Leslie", "Ron", "April")
colnames(parks_mat) <- c("Height", "Weight", "Income")
parks_mat[, "Height"]
```

```{r}
library("MASS")
Boston
```

```{r}
A <- matrix(1:6, nrow = 3, ncol = 2)
B <- c(1, 2)

A %*% B
A
B
```

##Free Response Practice for Midterm 2

###Number 1: NA column counts

```{r}
na_col_counts <- function(x) {
  result <- numeric(length(x))
  for(n in seq_len(length(x))) {
    for(i in seq_len(length(x[[n]]))) {
      if(is.na(x[[n]][i])) {
        result[n] <- result[n] + 1
      }
    }
  }
  result
}
library("MASS")
Cars93
na_col_counts(Cars93)
##Would this be ok???
```

##Number 2: Making each column of a matrix a unit vector

```{r}
unitize_mat <- function(X) {
  result <- matrix(0, nrow = nrow(X), ncol = ncol(X))
  for(n in seq_len(ncol(X))) {
    bottom <- sqrt(sum((X[, n])^2))
    for(i in seq_len(nrow(X))) {
      result[i, n] <- X[i, n] / bottom
    }
  }
  result
}
A <- cbind(c(1, 2, 3), c(1, 2, 3), c(1, 2, 3))
unitize_mat(A)
sqrt(1 + 4 + 9)
c(1, 2, 3) / sqrt(1 + 4 + 9)
```

##Number 3: Convert Adjancency Matrix to Adjacency List

```{r}
result <- list(length(4))
result[[1]] <- 3
result
adj_list <- function(X) {
  result <- list()
  for(j in seq_len(ncol(X))) {
    we_cool <- numeric(0)
    for(i in seq_len(nrow(X))) {
      if(!is.na(X[i, j])) {
      if(X[i, j] == 1) {
        we_cool <- c(we_cool, i)
      }
      }
    }
    result[[j]] <- we_cool
  }
  result
}
A <- cbind(c(NA, 1, 0, 1), c(1, NA, 1, 0), c(0, 1, NA, 1), c(1, 0, 1, NA))
adj_list(A)
##Figure out
##Got it (thumbs up)
```

##Number 4: Counting Fevers and putting them in a List

```{r}
fever_fn <- function(x) {
  result <- list()
  fever_names <- character(length(x))
  fever_count <- 0
  normal_count <- 0
  for(n in seq_len(length(x))) {
    if(x[n] < 100.4) {
       fever_names[n] <- "normal"
       normal_count <- normal_count + 1
    } else {
      fever_names[n] <- "fever"
      fever_count <- fever_count + 1
    }
  }
  table_name <- levels(as.factor(x))
  table_values <- numeric(length(table_name))
  for(i in seq_len(length(table_name))) {
    table_values[i] <- length(as.factor(x)[as.factor(x) == table_name[i]])
  }
    result$Child_Fever <- x
      names(result$Child_Fever) <- fever_names
    result$Table <- table_values
      names(result$Table) <- table_name
    result$Normal_Count <- normal_count
    result$Fever_Count <- fever_count
    result
}
fever_fn(c(96, 102, 97.8, 99.5, 100, 101, 103, 100, 96, 99.5, 96, 102, 104, 96, 102, 97.8, 99.5, 100, 101, 103, 100, 97, 99.5, 97, 102, 103))
```

##Answers

```{r}
##### Sample Exam 2
##### Free Response Solutions
##### Written by Michael Tsiang
##### NOT TO BE POSTED OR SHARED ANYWHERE

##### Question 1

na_col_counts <- function(df) {
  na_counter <- function(x) {
    sum(is.na(x))
  }
  vapply(df, na_counter, numeric(1))
}

na_col_counts2 <- function(df) {
  vapply(df, function(x) {
    sum(is.na(x))
  }, numeric(1))
}

library(MASS)
na_col_counts(Cars93)
na_col_counts2(Cars93)


##### Question 2

unitize_mat <- function(mat) {
  unitize <- function(v) {
    v / sqrt(sum(v^2))
  }
  apply(mat, 2, unitize)
}

unitize_mat2 <- function(mat) {
  apply(mat, 2, function(v) {
    v / sqrt(sum(v^2))
  })
}

trees_unit <- unitize_mat(trees)

magnitude <- function(v) {
  sqrt(sum(v^2))
}

apply(trees, 2, magnitude)
apply(trees_unit, 2, magnitude)


##### Question 3

# The predicate function is not necessary, but it is helpful
# to ensure that the input matrix is an adjacency matrix.

is_adj_mat <- function(mat) {
  is_square <- nrow(mat) == ncol(mat)
  if (!is_square) {
    stop("Not a square matrix")
  }
  sym <- matrix(, nrow(mat), ncol(mat))
  for (i in seq_len(nrow(mat))) {
    for (j in seq_len(ncol(mat))) {
      if (i != j) {
        sym[i, j] <- mat[i, j] == mat[j, i]
      } else {
        sym[i, j] <- is.na(mat[i, j])
      }
    }
  }
  vals <- levels(as.factor(mat))
  is_adj <- all(vals == c("0", "1")) || vals == "0" || vals == "1"
  is_square && all(sym) && is_adj
}

adj_list <- function(mat) {
  if (!is_adj_mat(mat)) {
    stop("Not an adjacency matrix")
  }
  out_list <- list()
  for (i in seq_len(nrow(mat))) {
    out_list[[i]] <- which(mat[i, ] == 1)
  }
  out_list
}

adj_list2 <- function(mat) {
  if (!is_adj_mat(mat)) {
    stop("Not an adjacency matrix")
  }
  mat_df <- as.data.frame(mat)
  out_list <- lapply(mat_df, function(x) {
    which(x == 1)
  })
  names(out_list) <- NULL
  out_list
}

adj_mat <- cbind(
  c(NA, 1, 0, 1), c(1, NA, 1, 0),
  c(0, 1, NA, 1), c(1, 0, 1, NA)
)
adj_list(adj_mat)
adj_list2(adj_mat)


##### Question 4

fever_fn <- function(x) {
  threshold <- 100.4
  fever <- x > threshold
  names(x)[!fever] <- "normal"
  names(x)[fever] <- "fever"
  list(
    "Child_Fever" = x,
    "Table" = table(x),
    "Normal_Count" = sum(!fever),
    "Fever_Count" = sum(fever)
  )
}

child_temps <- c(
  96, 102, 97.8, 99.5, 100, 101, 103, 100,
  96, 99.5, 96, 102, 104, 96, 102, 97.8, 99.5,
  100, 101, 103, 100, 97, 99.5, 97, 102, 103
)

fever_fn(child_temps)

```

###got them all right technically, but not ideal solutions -> USE APPLY FUNCTIONS MORE/GET THE HANG OF THEM

```{r}
X <- matrix(1:100, nrow = 20, ncol = 5)
X[c(1, 4, 5, 19), 4]
X
A <- matrix(1:6, nrow = 3, ncol = 2)
B <- matrix(1:6, nrow = 2, ncol = 3)
A %*% B
colSums(A)
rowSums(A)
colSums(B)
rowSums(B)
y <- factor(c(1, 2, 3, 2, 3, 1, 2, 3, 1, 2, 3, 2, 3, 2, 3, 2, 3, 1, 1, 1, 1, 2, 3, 3, 5))
y
table(y)
y[5:10, drop = TRUE]
row(A)
order(A)
rank(A)
z <- data.frame(list(c(1, 2, 3), c(5, 4, 3), c(3, 2, 7)), rownames = c("y", "u", "do"))
z[1, 2]
z
L <- list(matrix(1:4, nrow = 2, ncol = 2), c(2, 3, 5, 7), c("Yuh", "duh"))
L[[c(2, 3)]]
L
str(L)
lapply(L, mean)
sapply(L, mean)
vapply(L, mean, numeric(1))
```

```{r}
x <- c(0, 1, 2, 3, 4, 5, 1, 1, 2, 3, 1, 0, 2, 3, 1, 5)
y <- as.factor(x)
y + 1
```

##Acne Severity Data for at home vs. at UCLA

```{r}
#acne_data <- data.frame("Date" = c(000000, 000000, 000000, 120723), "Location" = c("Fremont", "UCLA", "Fremont", "UCLA"), "Count" = c(0, 0, 0, 2), "Severity" = c("None", "Severe", "Moderate", "Mild"), stringsAsFactors = TRUE)
##acne_data
#add_datapoint_acne_data <- function(date, location, count, severity) {
#  new_row <- list(date, location, count, severity)
#  rbind(acne_data, new_row) 
#}
#acne_data <- add_datapoint_acne_data(120823, "Fremont", 5, "Severe")
#acne_data ##works now!!
##delete 1st 3 rows
#acne_data <- acne_data[4, ]
#acne_data
#levels(acne_data$Location)
#levels(acne_data$Severity) ##yayyy okay all set up now
#acne_data <- add_datapoint_acne_data(120823, "UCLA", 3, "Mild")
##cancel out each entry after you do it, no need to rerun every time
#acne_data <- add_datapoint_acne_data(121023, "UCLA", 2, "Moderate")
#acne_data <- add_datapoint_acne_data(121123, "UCLA", 2, "Moderate")
##acne_data <- add_datapoint_acne_data(121223, "UCLA", 1, "Mild") ##Ahhhh R final
#acne_data <- add_datapoint_acne_data(121323, "UCLA", 2, "Mild")

```

##Stats 20 grade prediction estimate

```{r}
stats_20_grade <- function(homework, quizzes, exam1, exam2, exam3, discussion, campuswire) {
  homework <- mean(homework)
  quizzes <- mean(quizzes[-(quizzes == min(quizzes))])
  if(exam1 > exam2) {
    final_grade <- 0.15 * homework + 0.1 * quizzes + 0.25 * exam1 + 0.15 * exam2 + 0.3 * exam3 + 0.03 * discussion + 0.02 * campuswire
  } else {
    final_grade <- 0.15 * homework + 0.1 * quizzes + 0.15 * exam1 + 0.25 * exam2 + 0.3 * exam3 + 0.03 * discussion + 0.02 * campuswire
  }
  final_grade
}
stats_20_grade(100, c(100, 71, 75, 78, 100, 71, 71, 86, 90), 89.36, 90.59, 90, 100, 25) ##90% should be goal I guess, but aim for 100 of course
```

```{r}
library(caret)
```

```{r}
#final_dataset <- final_dataset[-29, ]
final_dataset
#From 101a final project
```

```{r}
cv_model <- train(Time ~ ., data = final_dataset, method = "lm", trControl = trainControl(method = "cv", number = 10))
```

```{r}
summary(cv_model)
```

